Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-10 SupportingInformation.Rmd
modified

\newpage
```{r tab_soilCN_asym,echo=F,results="markup"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_soilCN_asym<-make_table_stat_fn(data=stat_soilCN_ga)
knitr::kable(tab_soilCN_asym, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption = "**Soil CN data set results** for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis. Three statistics are listed in the left column that measured asymmetry of tail dependence by comparing the distribution ranges $0-0.1$ and $0.9-1$ (see \\nameref{MT-NPA}). One thousand Kendall-preserving and 1000 Spearman-preserving surrogates with normal copula structure were created, and the same statistics were computed for the surrogates. A table entry $<N$ indicates the value of the given statistic on the data was less than its value on $N$ of the surrogates, so entries of the form $<X$ for $X$ equal to $975$ or above indicate that upper-tail dependence was significantly stronger than lower-tail dependence.\\label{tab_soilCN_asym}")
#kable_styling(, position = "float_left")
```

@@

<!--Display model selection results for BMR:birds data in a table-->
```{r tab_bmr_mammals_fit, echo=F, results='markup'}
h<-BivMS_mammals$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for **mammals' BMR dataset** . \\label{tab_bmr_mammals_fit}",
             booktabs=T)
```

@@

```{r tab_count_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_count),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for **abundances of the green spruce aphid**, for comparison with Table \\ref{tab_count_AICw}. \\label{tab_count_AICw_normal}",
             booktabs=TRUE
             )
```

@@

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
knitr::kable(summary_stat[,c(1:4)], booktabs = T, 
             format = "pandoc",
             digits=3,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asym. sensitivity \\label{tab_summary_stat_asym_sens}")
```

@@

```{r tab_stat_npa_asym_1,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[1]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[1]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_1}"))
```

@@

\newpage
<!--results='hide'-->
```{r skewness_aphidcount_allsp_plot, echo=F, results="hide", warning=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

@@

![Extinction_Risk_local_dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp}](./Results/ext_risk_local_disp.pdf){ width=40%, height=40% }

![Extinction_Risk_global_dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp}](./Results/ext_risk_global_disp.pdf){ width=40%, height=40% }

![Extinction_Risk_numlocs_effect_local_disp; numsteps=25, numsims=10000\label{fig_risk_numlocs_effect_local_disp}](./Results/ext_risk_numlocs_effect_local_disp.pdf){ width=40%, height=40% }

![Extinction_Risk_numlocs_effect_global_disp; numsteps=25, numsims=10000\label{fig_risk_numlocs_effect_global_disp}](./Results/ext_risk_numlocs_effect_global_disp.pdf){ width=40%, height=40% }

![Extinction_Risk_K_effect on Ricker model; r=0.25, numsteps=25, numsims=10000\label{fig_risk_K_effect}](./Results/ext_risk_K_effect.pdf){ width=40%, height=40% }

>>>>

```{r tab_soilCN_asym,echo=F,results="markup"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_soilCN_asym<-make_table_stat_fn(data=stat_soilCN_ga)
knitr::kable(tab_soilCN_asym, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption = "**Soil CN data set results** for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis. Three statistics are listed in the left column that measured asymmetry of tail dependence by comparing the distribution ranges $0-0.1$ and $0.9-1$ (see \\nameref{MT-NPA}). One thousand Kendall-preserving and 1000 Spearman-preserving surrogates with normal copula structure were created, and the same statistics were computed for the surrogates. A table entry $<N$ indicates the value of the given statistic on the data was less than its value on $N$ of the surrogates, so entries of the form $<X$ for $X$ equal to $975$ or above indicate that upper-tail dependence was significantly stronger than lower-tail dependence.\\label{tab_soilCN_asym}")
#kable_styling(, position = "float_left")
```

@@

\newpage
<!--Display model selection results for BMR:birds data in a table-->
```{r tab_bmr_mammals_fit, echo=F, results='markup'}
h<-BivMS_mammals$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for **mammals' BMR dataset** . \\label{tab_bmr_mammals_fit}",
             booktabs=T)
```

@@

\newpage
```{r tab_count_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_count),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for **abundances of the green spruce aphid**, for comparison with Table \\ref{tab_count_AICw}. \\label{tab_count_AICw_normal}",
             booktabs=TRUE
             )
```

@@

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
summary_stat<-summary_stat[,c(1:4)]
rownames(summary_stat)<-c("bestcop.AICw","N.AICw","relLTdep.AICw","relUTdep.AICw","p.CvM","p.KS","BS.success.percent")
knitr::kable(summary_stat, booktabs = T, 
             format = "pandoc",
             digits=3,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asymmetric sensitivity : \\textbf{bestcop.AICw} and \\textbf{N.AICw} represent the AIC-weightage for best fit copula and Normal copula, \\textbf{relLTdep.AICw} and \\textbf{relLTdep.AICw} represent relative lower tail and upper tail dependence based on AIC-weightage respectively, \\textbf{p.CvM} and \\textbf{p.KS} are the p-values coming from goodness of fit test (Cramer-von Mises and Kolmogorov-Smirnov statistics based), \\textbf{BS.success.percent} percentage of successful bootstraps in goodness of fit test. Each column summarizes those statistics for each copula plotted in Fig. \\ref{MT-fig_ms_asym_b_0.1}.\\label{tab_summary_stat_asym_sens}")
```

@@

\newpage
```{r tab_stat_npa_asym_1,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[1]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[1]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_1}"))
```

@@

<!--results='hide'-->
```{r skewness_aphidcount_allsp_plot, echo=F, results="hide", warning=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Lewton-Cohen model : $r=0$, Ricker model : $r\neq0$) with local dispersion (see Eq. \ref{eq.extrisk_model}); numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp}](./Results/ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Lewton-Cohen model : $r=0$, Ricker model : $r\neq0$) with global dispersion (see Eq. \ref{eq.extrisk_model}); numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp}](./Results/ext_risk_global_disp.pdf){ width=40%, height=40% }

![Increasing patch number allows metapopulation to disperse more efficiently and thereby decresing extinction risk calculated after 25 years; models with local dispersion with numsims=10000 (see Eq. \ref{eq.extrisk_model}).\label{fig_risk_numlocs_effect_local_disp}](./Results/ext_risk_numlocs_effect_local_disp.pdf){ width=40%, height=40% }

![Increasing patch number allows metapopulation to disperse more efficiently and thereby decresing extinction risk calculated after 25 years; models with global dispersion with numsims=10000 (see Eq. \ref{eq.extrisk_model}).\label{fig_risk_numlocs_effect_global_disp}](./Results/ext_risk_numlocs_effect_global_disp.pdf){ width=40%, height=40% }

![Extinction risk as calculated after 25 years on Ricker model (r=0.25, numsims=10000) decreases as carrying capacity $K$ increases for both local and global dispersion (see Eq. \ref{eq.extrisk_model}).\label{fig_risk_K_effect}](./Results/ext_risk_K_effect.pdf){ width=40%, height=40% }
